Integrative forecasting of seasonal influenza A/H3N2 by genotype and phenotype

### 2019-07-19 manuscript/main.tex
Clarify equation for distance to the future
Use more standard representation of double sums, use time parameters to
indicate which timepoints each set of strains come from, and add delta time to
the fitness parameter.

For a model based on any given combination of fitness metrics, we found the fitness coefficients that minimized the mean weighted Hamming distance between the estimated and observed future populations as defined by,

$$
\Delta(X(t + \Delta{t}), \hat{X}(t + \Delta{t})) = \frac{(\sum_{i}x_{i}\exp(f_{i}(t))(\sum_{j}x_{j}d_{i,j})) - (\sum_{j}x_{j}(\sum_{j'}x_{j'}d_{j,j'}))}{(\sum_{i}x_{i}(\sum_{j}x_{j}d_{i,j}))},
$$

where the first term in the numerator measures the mean distance between estimated and observed populations, the second term accounts for the diversity of the future population, and the denominator accounts for the diversity between the current and future populations.
When the sequence diversity of the estimated and observed future populations are equal, the metric evaluates to zero.
When the estimated sequence diversity is closer to the center of the future population's observed diversity, the metric evaluates to a negative proportion.
We applied the Nelder-Mead minimization algorithm as implemented in SciPy \cite{SciPy} to learn fitness coefficients that minimize the average of this distance metric over all timepoints in a given training window.

>>>>

For a model based on any given combination of fitness metrics, we found the fitness coefficients that minimized the mean weighted Hamming distance between the estimated and observed future populations at time $u = t + \Delta{t}$ as defined by,

$$
\Delta(X(u), \hat{X}(u)) = \frac{\sum_{i}\sum_{j}x_{i}(t)\exp(f_{i}(t)\Delta{t})x_{j}(u)d_{i,j} - \sum_{j}\sum_{k}x_{j}(u)x_{k}(u)d_{j,k}}{\sum_{i}\sum_{j}x_{i}(t)x_{j}(u)d_{i,j}}.
$$

The first term in the numerator measures the mean distance between estimated and observed future populations, the second term measures the average distance of the future population to itself, and the denominator measures the average distance between the current and future populations.
When a model accurately estimates the average distance of the future population to itself, the metric evaluates to zero.
When the estimated sequence diversity is closer to the center of the future population's observed diversity, the metric evaluates to a negative proportion.
We applied the Nelder-Mead minimization algorithm as implemented in SciPy \cite{SciPy} to learn fitness coefficients that minimize the average of this distance metric over all timepoints in a given training window.
